An interactive environment for mapping computational structures to FPGAs

### 2016-07-07 paper/paper.tex
Added figure about HOFs
Wrote paragraph about hardware generation.

  The main advantage of using computational structures is that there is no need to perform dependency analysis of for-loops.
  Since all dependencies are known, computations can be distributed over space and time by mathematical transformation rules.
  Even though no standard C for-loops are used to express repetitive computations, this should not be a problem for programmers since similar patters are also used in map-reduce applications.
  Figure XXXXXXX shows two examples of computational structures: the higher-order function \emph{zipWith} and \emph{foldl}.
  Using \emph{zipWith} an operation is applied to pairs from two lists while \emph{foldl} reduces all elements in a list to one element.

  \missingfigure{plaatje zipw en foldl hier}

@@

  \todo[inline]{hardware generation using \clash \cite{Baaij10}}
  nodes become combinational components and edges are implemented as FIFOs.....
  The code is generated using \clash, a functional hardware description language.
  each node has a peace of \clash code that represents the functionality of the node.....

>>>>

  The main advantage of using computational structures is that there is no need to perform dependency analysis of for-loops.
  Since all dependencies are known, computations can be distributed over space and time by mathematical transformation rules.
  Even though no standard C for-loops are used to express repetitive computations, this should not be a problem for programmers since similar patters are also used in map-reduce applications.
  Figure \ref{fig:zipwthandfoldlstruct} shows two examples of computational structures: the higher-order function \emph{zipWith} and \emph{foldl}.
  Using \emph{zipWith} an operation is applied to pairs from two lists while \emph{foldl} reduces all elements in a list to one element.

  \begin{figure}[h!]
    \centering
    \includegraphics[width=3in]{HOFs}
    \caption{Structure of \emph{zipWith} and \emph{foldl}}
    \label{fig:zipwthandfoldlstruct}
  \end{figure}

@@

  During hardware generation, each node is implemented as a combinational circuit containing the functionality of the node and logic for producing and consuming data.
  The edges, on the other hand, are implemented as FIFOs.
  The code is generated using \clash, a functional hardware description language~\cite{Baaij10}.
  Additional to the python code that can be put in a node for simulation, \clash\ code is added for the implementation on hardware.
